---
title: "Aggregation"
# output: html_notebook
author:
  - name: Qiuping Ma
date: "`r Sys.Date()`"
# creative_commons: CC BY-NC
output:
  html_notebook:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: paper
    highlight: tango
    chunk_output_type: inline
---
# Introduction
With the results of 6 MCDM methods, now we move to the step of aggregation. The aggregation is based on the idea that a combination of different MCDM methods can provide a robust and comprehensive result. Even though we calculate the differences between various MCDM methods, there is no sufficient evidence shows that the specific method with the largest difference outputs the least reliable results. Therefore, all the reuslts of the 6 MCDM methods are served as the input of the aggregation.

We propose a new aggregated approach from the machine learning perspective in which four well-known loss functions are integrated with the results obatined from former step.

# Preparation
## Set working directory and load the package
For operation simplicity, we set the working directory as below.
```{r}
setwd("C:/Users/au630301/Documents/00.Qiuping/2nd Paper/code")
getwd()
```
```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if(!require("Metrics")) install.packages("Metrics")
library("Metrics")
if(!require("pracma")) install.packages("pracma")
library("pracma")
```
## Load the data set
```{r eval = FALSE}
MCDM_result_norm_new <- read_csv("processed4/MCDM_result_norm_new.csv")
# MCDM_result_norm_new
```
```{r}
agg_sr_df  <- MCDM_result_norm_new[,c(2:7)]
agg_pi_df  <- MCDM_result_norm_new[,c(8:13)]
agg_sw_df  <- MCDM_result_norm_new[,c(14:19)]
agg_sqc_df <- MCDM_result_norm_new[,c(20:25)]
# agg_sr_df
```
# Aggregation
## learning rate and Initial weight setting
We test 3 learning rate: 1, 0.1, and 0.01.
We test 100 different scenarios of criteria weight.
```{r}
# Learning rate setting
learn_rate <- c(1, 0.1, 0.01)
```

```{r}
# Initial weight setting
set.seed(123)
scen_no <- 100
initial_weight <- matrix(NA, scen_no, 6)
for (i in 1:scen_no) {
  initial_weight[i,] = prop.table(runif(6))
}
write_csv(as.data.frame(initial_weight), "processed4/initial_weight.csv" )
```
## L2 loss function
### Load the package
```{r}
if(!require("optimx")) install.packages("optimx")
library("optimx")
```
```{r}
# Optimization model format
#optimx(par, fn, gr=Null, Hess=Null, lower=inf,
       #upper=inf, method='', itnmax=Null, ...)
```
### Supply risk
```{r}
# set up the optimization function
fn_L2_sr <- function(A){
  vector.A <- A
  
  Y <- as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,1])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,2])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,3])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,4])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,5])))^2) + 
       as.numeric(stats::dist(rbind(vector.A, t(agg_sr_df[,6])))^2)
  return(Y)
}
```
```{r}
# calculation
optimx(rep(0, times = nrow(agg_sr_df)),fn_L2_sr, method = c("Nelder-Mead", "CG", "BFGS", "spg", "nlm"))
agg_sr_L2 <- optimx(rep(0, times = nrow(agg_sr_df)),fn_L2_sr, method = "CG")
# agg_sr_L2
```
### Profit impact
```{r}
# set up the optimization function
fn_L2_pi <- function(A){
  vector.A <- A
  
  Y <- as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,1])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,2])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,3])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,4])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,5])))^2) + 
       as.numeric(stats::dist(rbind(vector.A, t(agg_pi_df[,6])))^2)
    
  return(Y)
}
```
```{r}
# calculation
optimx(rep(0, times = nrow(agg_pi_df)),fn_L2_pi, method = c("Nelder-Mead", "CG", "BFGS", "spg", "nlm"))
agg_pi_L2 <- optimx(rep(0, times = nrow(agg_pi_df)),fn_L2_pi, method = "CG")
```
### Supplier willingness
```{r}
# set up the optimization function
fn_L2_sw <- function(A){
  vector.A <- A
  
  Y <- as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,1])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,2])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,3])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,4])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,5])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sw_df[,6])))^2)
    
  return(Y)
}
```
```{r}
# calculation
optimx(rep(0, times = nrow(agg_sw_df)),fn_L2_sw, method = c("Nelder-Mead", "CG", "BFGS", "spg", "nlm"))
agg_sw_L2 <- optimx(rep(0, times = nrow(agg_sw_df)),fn_L2_sw, method = "CG")
```
### Supplier quality capability
```{r}
# set up the optimizatin function
fn_L2_sqc <- function(A){
  vector.A <- A
  
  Y <- as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,1])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,2])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,3])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,4])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,5])))^2) +
       as.numeric(stats::dist(rbind(vector.A, t(agg_sqc_df[,6])))^2)
    
  return(Y)
}
```
```{r}
# calculation
optimx(rep(0, times = nrow(agg_sqc_df)),fn_L2_sqc, method = c("Nelder-Mead", "CG", "BFGS", "spg", "nlm"))
agg_sqc_L2 <- optimx(rep(0, times = nrow(agg_sqc_df)),fn_L2_sqc, method = "CG")
```
### Result summary
```{r}
Supplier_ID <- c("A_{01}", "A_{02}", "A_{03}", "A_{04}", "A_{05}","A_{06}", "A_{07}", "A_{08}", "A_{09}", "A_{10}",
                 "A_{11}", "A_{12}", "A_{13}", "A_{14}", "A_{15}","A_{16}", "A_{17}", "A_{18}", "A_{19}", "A_{20}",
                 "A_{21}", "A_{22}", "A_{23}", "A_{24}", "A_{25}","A_{26}", "A_{27}", "A_{28}", "A_{29}", "A_{30}",
                 "A_{31}", "A_{32}", "A_{33}", "A_{34}", "A_{35}","A_{36}", "A_{37}", "A_{38}", "A_{39}", "A_{40}",
                 "A_{41}", "A_{42}", "A_{43}", "A_{44}", "A_{45}","A_{46}", "A_{47}", "A_{48}", "A_{49}", "A_{50}",
                 "A_{51}", "A_{52}", "A_{53}", "A_{54}", "A_{55}","A_{56}", "A_{57}", "A_{58}", "A_{59}", "A_{60}",
                 "A_{61}", "A_{62}", "A_{63}", "A_{64}", "A_{65}","A_{66}", "A_{67}", "A_{68}", "A_{69}", "A_{70}",
                 "A_{71}", "A_{72}", "A_{73}", "A_{74}", "A_{75}","A_{76}", "A_{77}", "A_{78}", "A_{79}", "A_{80}",
                 "A_{81}", "A_{82}", "A_{83}", "A_{84}", "A_{85}","A_{86}", "A_{87}", "A_{88}", "A_{89}", "A_{90}",
                 "A_{91}", "A_{92}", "A_{93}", "A_{94}", "A_{95}","A_{96}", "A_{97}", "A_{98}", "A_{99}", "A_{100}"
)  
```
```{r}
agg_L2 <- cbind(as.data.frame(Supplier_ID),unlist(matrix(agg_sr_L2[1:nrow(MCDM_result_norm_new)])),unlist(matrix(agg_pi_L2[1:nrow(MCDM_result_norm_new)])),unlist(matrix(agg_sw_L2[1:nrow(MCDM_result_norm_new)])),unlist(matrix(agg_sqc_L2[1:nrow(MCDM_result_norm_new)])))

colnames(agg_L2, do.NULL = TRUE, prefix = "col")
colnames(agg_L2) <- c("Supplier_ID", "Supplier_risk","Profit_impact", "Supplier_willingness", "Supplier_quality_capability" )

write_csv(as.data.frame(agg_L2), "processed4/agg_L2.csv" )
agg_L2
```
L2 loss function has a closed-form solution. Thus, L2 loss function yields identical weight for each MDM method being-used. This is because the optimal weight vector will be the averaged weight vector when setting the derivative of L2 loss function to be zero.
## L1 loss function
### Set up function
#### Iteration function
```{r}
Fn_L1 <- function(A, B, C){
  vector.w <- A
  matrix.Y <- as.matrix(B)
  method_no <- ncol(matrix.Y)
  alt_no <- nrow(matrix.Y)
  vector.z <- matrix.Y %*% vector.w
  learning_rate <- C
  
  # parameter initialization
  tol <- 10e-10 # tolerance based on which the main loop is terminated
  iter_max <- 10e5 # maximum number of iteration
  t <- 0        # iteration indicator
  Error_ae_sum <- rep(0,times = alt_no)
  g <- rep(0,times = method_no)
  w <- rep(0,times = method_no)
  
  while(t < iter_max){
    Error <- matrix.Y - repmat(vector.z,1,method_no)
    Error_ae <- abs(Error)
    Error_ae_divid <- Error/Error_ae
    Error_ae_divid[is.na(Error_ae_divid)] <- 0
    
    for (i in 1: alt_no) {
      Error_ae_sum[i] <- sum(Error_ae_divid[i,])
    }
    
    for (k in 1: method_no) {
      g[k] <- sum(Error_ae_sum * matrix.Y[,k])/(method_no * alt_no)*learning_rate
    }
    
    # update weight
    w <- vector.w- g
    vector.w_old <- vector.w
    for (k in 1: method_no) {
      vector.w[k] <- w[k] / sum(w)
    }
    
    # update vector.z
    vector.z_old <- vector.z
    vector.z <- matrix.Y %*% vector.w
    
    # convergence conditions
    if(norm(matrix(vector.w-vector.w_old), "2") < tol && norm(matrix(vector.z-vector.z_old), "2") < tol ){
      break
    }
    
    if(any(vector.w < 0)){
      break
    }
    
    # update iteration
    t = t + 1
    
    # if(t == 10000){
    #   break
    # }
    
  }
  output_list <- list("iteration" = t, "g" = g, "w" = w,"vector.w_old" = vector.w_old, "vector.w" = vector.w, "vector.z"  = vector.z, "vector.z_old"  = vector.z_old, "Error" = Error,"Error_ae" = Error_ae, "Error_ae_sum" = Error_ae_sum)
  
  return(output_list)
}
```
#### Cost function
```{r}
Fn_L1_cost <- function(A, B){
  vector.z <- as.matrix(A)
  matrix.Y <- as.matrix(B)
  
  J <- rep(0,times = ncol(matrix.Y))
  for (i in 1: ncol(matrix.Y)) {
    J[i] <- sum(ae(vector.z, matrix.Y[,i]))
  }
  cost <- sum(J)/(ncol(matrix.Y)*nrow(matrix.Y))
}
```
### Supply risk
#### Run the iteration function 
```{r}
# initialization
L1_sr_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
L1_sr_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
L1_sr_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sr_df))
# run the function
for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  L1_sr  <- Fn_L1(matrix(data.matrix(initial_weight[j,])), agg_sr_df,learn_rate[i] )
  end_time <- Sys.time()
  L1_sr_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  L1_sr_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sr[4]))
  L1_sr_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sr[7]))
  }
}

# save the result
# write_csv(as.data.frame(L1_sr_time), "processed4/L1_sr_time.csv" )
write_csv(as.data.frame(L1_sr_w), "processed4/L1_sr_w.csv" )
write_csv(as.data.frame(L1_sr_z), "processed4/L1_sr_z.csv" )
```
#### Run the cost function
```{r}
L1_sr_cost <- rep(0,times = nrow(L1_sr_z))
for (i in 1:nrow(L1_sr_z)) {
  A <- data.matrix(L1_sr_z[i,])
  L1_sr_cost[i] <- Fn_L1_cost(A, agg_sr_df)
}
# L1_sr_cost
# write_csv(as.data.frame(L1_sr_cost), "processed4/L1_sr_cost.csv" )
```
#### Cost and time summary
```{r}
L1_sr_cost_summary <- matrix(L1_sr_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(L1_sr_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sr_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

L1_sr_time_summary <- matrix(L1_sr_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(L1_sr_time_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sr_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(L1_sr_cost_summary), "processed4/L1_sr_cost_summary.csv" )
write_csv(as.data.frame(L1_sr_time_summary), "processed4/L1_sr_time_summary.csv" )
```
### Profit impact
#### Run the iteration function
```{r}
# initialization
L1_pi_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
L1_pi_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
L1_pi_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_pi_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  L1_pi  <- Fn_L1(matrix(data.matrix(initial_weight[j,])), agg_pi_df,learn_rate[i] )
  end_time <- Sys.time()
  L1_pi_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  L1_pi_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_pi[4]))
  L1_pi_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_pi[7]))
  }
}
# save the result
# write_csv(as.data.frame(L1_pi_time), "processed4/L1_pi_time.csv" )
write_csv(as.data.frame(L1_pi_w), "processed4/L1_pi_w.csv" )
write_csv(as.data.frame(L1_pi_z), "processed4/L1_pi_z.csv" )
```

#### Run the cost function 
```{r}
L1_pi_cost <- rep(0,times = nrow(L1_pi_z))
for (i in 1:nrow(L1_pi_z)) {
  A <- data.matrix(L1_pi_z[i,])
  L1_pi_cost[i] <- Fn_L1_cost(A, agg_pi_df)
}
# L1_pi_cost
# write_csv(as.data.frame(L1_pi_cost), "processed4/L1_pi_cost.csv" )
```
#### Cost and time summary
```{r}
L1_pi_cost_summary <- matrix(L1_pi_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(L1_pi_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_pi_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

L1_pi_time_summary <- matrix(L1_pi_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(L1_pi_time_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_pi_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(L1_pi_cost_summary), "processed4/L1_pi_cost_summary.csv" )
write_csv(as.data.frame(L1_pi_time_summary), "processed4/L1_pi_time_summary.csv" )
```
### Supplier willingness
#### Run the iteration function
```{r}
# initialization
L1_sw_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
L1_sw_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
L1_sw_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sw_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  L1_sw  <- Fn_L1(matrix(data.matrix(initial_weight[j,])), agg_sw_df,learn_rate[i] )
  end_time <- Sys.time()
  L1_sw_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  L1_sw_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sw[4]))
  L1_sw_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sw[7]))
  }
}
# save the result
# write_csv(as.data.frame(L1_sw_time), "processed4/L1_sw_time.csv" )
write_csv(as.data.frame(L1_sw_w), "processed4/L1_sw_w.csv" )
write_csv(as.data.frame(L1_sw_z), "processed4/L1_sw_z.csv" )
```

#### Run the cost function
```{r}
L1_sw_cost <- rep(0,times = nrow(L1_sw_z))
for (i in 1:nrow(L1_sw_z)) {
  A <- data.matrix(L1_sw_z[i,])
  L1_sw_cost[i] <- Fn_L1_cost(A, agg_sw_df)
}
# L1_sw_cost
# write_csv(as.data.frame(L1_sw_cost), "processed4/L1_sw_cost.csv" )
```

#### Cost and time summary
```{r}
L1_sw_cost_summary <- matrix(L1_sw_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(L1_sw_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sw_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

L1_sw_time_summary <- matrix(L1_sw_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(L1_sw_time_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sw_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(L1_sw_cost_summary), "processed4/L1_sw_cost_summary.csv" )
write_csv(as.data.frame(L1_sw_time_summary), "processed4/L1_sw_time_summary.csv" )
```
### Supplier quality capability
#### Run the iteration function
```{r}
# initialization
L1_sqc_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
L1_sqc_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
L1_sqc_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sqc_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  L1_sqc  <- Fn_L1(matrix(data.matrix(initial_weight[j,])), agg_sqc_df,learn_rate[i] )
  end_time <- Sys.time()
  L1_sqc_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  L1_sqc_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sqc[4]))
  L1_sqc_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(L1_sqc[7]))
  }
}

# save the result
# write_csv(as.data.frame(L1_sqc_time), "processed4/L1_sqc_time.csv" )
write_csv(as.data.frame(L1_sqc_w), "processed4/L1_sqc_w.csv" )
write_csv(as.data.frame(L1_sqc_z), "processed4/L1_sqc_z.csv" )
```

#### Run the cost function
```{r}
L1_sqc_cost <- rep(0,times = nrow(L1_sqc_z))
for (i in 1:nrow(L1_sqc_z)) {
  A <- data.matrix(L1_sqc_z[i,])
  L1_sqc_cost[i] <- Fn_L1_cost(A, agg_sqc_df)
}
# L1_sqc_cost
# write_csv(as.data.frame(L1_sqc_cost), "processed3/L1_sqc_cost.csv" )
```

#### Cost and time summary
```{r}
L1_sqc_cost_summary <- matrix(L1_sqc_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(L1_sqc_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sqc_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

L1_sqc_time_summary <- matrix(L1_sqc_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(L1_sqc_time_summary, do.NULL = TRUE, prefix = "col")
colnames(L1_sqc_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(L1_sqc_cost_summary), "processed4/L1_sqc_cost_summary.csv" )
write_csv(as.data.frame(L1_sqc_time_summary), "processed4/L1_sqc_time_summary.csv" )
```
## Log-cosh (LC) loss function
### Set up function
#### Iteration function
```{r}
Fn_LC <- function(A, B, C){
  vector.w <- A
  matrix.Y <- as.matrix(B)
  method_no <- ncol(matrix.Y)
  alt_no <- nrow(matrix.Y)
  vector.z <- matrix.Y %*% vector.w
  learning_rate <- C
  
  # parameter initialization 
  tol <- 10e-10 # tolerance based on which the main loop is terminated
  iter_max <- 10e5 # maximum number of iteration
  t <- 0        # iteration indicator
  Error_tanh_sum <- rep(0,times = alt_no)
  g <- rep(0,times = method_no)
  w <- rep(0,times = method_no)
  
  while(t < iter_max){
    Error <- matrix.Y - repmat(vector.z,1,method_no)
    Error_tanh <- tanh(Error)
    
    for (i in 1: alt_no) {
      Error_tanh_sum[i] <- sum(Error_tanh[i,])
    }
    
    for (k in 1: method_no) {
      g[k] <- sum(Error_tanh_sum * matrix.Y[,k])/(method_no * alt_no)*learning_rate
    }
    
    # update weight
    w <- vector.w- g
    vector.w_old <- vector.w
    for (k in 1: method_no) {
      vector.w[k] <- w[k] / sum(w)
    }
    
    # update vector.z
    vector.z_old <- vector.z
    vector.z <- matrix.Y %*% vector.w
    
    # convergence conditions
    if(norm(matrix(vector.w-vector.w_old), "2") < tol && norm(matrix(vector.z-vector.z_old), "2") < tol ){
      break
    }
    
    if(any(vector.w < 0)){
      break
    }
    
    # update iteration
    t = t + 1
    # if(t == 1){
    #   break
    # }
  }
  output_list <- list("iteration" = t, "g" = g, "vector.w_old" = vector.w_old, "vector.w" = vector.w, "vector.z"  = vector.z, "vector.z_old"  = vector.z_old, "Error" = Error,"Error_tanh" = Error_tanh, "Error_tanh_sum" = Error_tanh_sum)
  
  return(output_list)
}
```
#### Cost function
```{r}
Fn_LC_cost <- function(A, B){
  vector.z <- as.matrix(A)
  matrix.Y <- as.matrix(B)
  
  J <- rep(0,times = ncol(matrix.Y))
  for (i in 1: ncol(matrix.Y)) {
    J[i] <- sum(log(cosh(vector.z - matrix.Y[,i]),exp(1)))
  }
  cost <- sum(J)/(ncol(matrix.Y)*nrow(matrix.Y))
}
```
### Supply risk
#### Run the iteration function
```{r}
# initialization
LC_sr_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
LC_sr_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
LC_sr_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sr_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  LC_sr  <- Fn_LC(matrix(data.matrix(initial_weight[j,])), agg_sr_df,learn_rate[i] )
  end_time <- Sys.time()
  LC_sr_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  LC_sr_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sr[3]))
  LC_sr_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sr[6]))
  }
}
# save the result
# write_csv(as.data.frame(LC_sr_time), "processed4/LC_sr_time.csv" )
write_csv(as.data.frame(LC_sr_w), "processed4/LC_sr_w.csv" )
write_csv(as.data.frame(LC_sr_z), "processed4/LC_sr_z.csv" )
```

#### Run the cost function
```{r}
LC_sr_cost <- rep(0,times = nrow(LC_sr_z))
for (i in 1:nrow(LC_sr_z)) {
  A <- data.matrix(LC_sr_z[i,])
  LC_sr_cost[i] <- Fn_LC_cost(A, agg_sr_df)
}
#LC_sr_cost
# write_csv(as.data.frame(LC_sr_cost), "processed4/LC_sr_cost.csv" )
```

#### Cost and time summary
```{r}
LC_sr_cost_summary <- matrix(LC_sr_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(LC_sr_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sr_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

LC_sr_time_summary <- matrix(LC_sr_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(LC_sr_time_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sr_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(LC_sr_cost_summary), "processed4/LC_sr_cost_summary.csv" )
write_csv(as.data.frame(LC_sr_time_summary), "processed4/LC_sr_time_summary.csv" )
```
### Profit impact
#### Run the iteration function
```{r}
# initialization
LC_pi_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
LC_pi_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
LC_pi_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_pi_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  LC_pi  <- Fn_LC(matrix(data.matrix(initial_weight[j,])), agg_pi_df,learn_rate[i] )
  end_time <- Sys.time()
  LC_pi_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  LC_pi_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_pi[3]))
  LC_pi_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_pi[6]))
  }
}
# save the result
# write_csv(as.data.frame(LC_pi_time), "processed4/LC_pi_time.csv" )
write_csv(as.data.frame(LC_pi_w), "processed4/LC_pi_w.csv" )
write_csv(as.data.frame(LC_pi_z), "processed4/LC_pi_z.csv" )
```

#### Run the cost function
```{r}
# calculate the cost for each setting
LC_pi_cost <- rep(0,times = nrow(LC_pi_z))
for (i in 1:nrow(LC_pi_z)) {
  A <- data.matrix(LC_pi_z[i,])
  LC_pi_cost[i] <- Fn_LC_cost(A, agg_pi_df)
}
#LC_pi_cost
#write_csv(as.data.frame(LC_pi_cost), "processed3/LC_pi_cost.csv" )
```

#### Cost and time summary
```{r}
LC_pi_cost_summary <- matrix(LC_pi_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(LC_pi_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_pi_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

LC_pi_time_summary <- matrix(LC_pi_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(LC_pi_time_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_pi_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(LC_pi_cost_summary), "processed4/LC_pi_cost_summary.csv" )
write_csv(as.data.frame(LC_pi_time_summary), "processed4/LC_pi_time_summary.csv" )
```
### Supplier willingness
#### Run the iteration function
```{r}
# initialization
LC_sw_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
LC_sw_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
LC_sw_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sw_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  LC_sw  <- Fn_LC(matrix(data.matrix(initial_weight[j,])), agg_sw_df,learn_rate[i] )
  end_time <- Sys.time()
  LC_sw_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  LC_sw_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sw[3]))
  LC_sw_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sw[6]))
  }
}
# save the result
# write_csv(as.data.frame(LC_sw_time), "processed4/LC_sw_time.csv" )
write_csv(as.data.frame(LC_sw_w), "processed4/LC_sw_w.csv" )
write_csv(as.data.frame(LC_sw_z), "processed4/LC_sw_z.csv" )
```
#### Run the cost function
```{r}
LC_sw_cost <- rep(0,times = nrow(LC_sw_z))
for (i in 1:nrow(LC_sw_z)) {
  A <- data.matrix(LC_sw_z[i,])
  LC_sw_cost[i] <- Fn_LC_cost(A, agg_sw_df)
}
# LC_sw_cost
# write_csv(as.data.frame(LC_sw_cost), "processed3/LC_sw_cost.csv" )
```

#### Cost and time summary
```{r}
LC_sw_cost_summary <- matrix(LC_sw_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(LC_sw_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sw_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

LC_sw_time_summary <- matrix(LC_sw_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(LC_sw_time_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sw_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(LC_sw_cost_summary), "processed4/LC_sw_cost_summary.csv" )
write_csv(as.data.frame(LC_sw_time_summary), "processed4/LC_sw_time_summary.csv" )
```
### Supplier quality capability
#### Run the iteration function
```{r}
# initialization
LC_sqc_time <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = 1)
LC_sqc_w <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = ncol(initial_weight))
LC_sqc_z <- matrix(, nrow = nrow(initial_weight)*length(learn_rate), ncol = nrow(agg_sqc_df))

for (i in 1:length(learn_rate)) {
  for (j in 1:nrow(initial_weight)) {
  start_time <- Sys.time()
  LC_sqc  <- Fn_LC(matrix(data.matrix(initial_weight[j,])), agg_sqc_df,learn_rate[i] )
  end_time <- Sys.time()
  LC_sqc_time[j + nrow(initial_weight) *(i-1),] <- end_time - start_time
  LC_sqc_w[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sqc[3]))
  LC_sqc_z[j + nrow(initial_weight) *(i-1),] <- matrix(unlist(LC_sqc[6]))
  }
}
# save the result
# write_csv(as.data.frame(LC_sqc_time), "processed4/LC_sqc_time.csv" )
write_csv(as.data.frame(LC_sqc_w), "processed4/LC_sqc_w.csv" )
write_csv(as.data.frame(LC_sqc_z), "processed4/LC_sqc_z.csv" )
```

#### Run the cost function
```{r}
# calculate the cost for each setting
LC_sqc_cost <- rep(0,times = nrow(LC_sqc_z))
for (i in 1:nrow(LC_sqc_z)) {
  A <- data.matrix(LC_sqc_z[i,])
  LC_sqc_cost[i] <- Fn_LC_cost(A, agg_sqc_df)
}
# LC_sqc_cost
# write_csv(as.data.frame(LC_sqc_cost), "processed4/LC_sqc_cost.csv" )
```

#### Cost and time summary
```{r}
LC_sqc_cost_summary <- matrix(LC_sqc_cost,nrow = nrow(initial_weight), ncol = length(learn_rate))
colnames(LC_sqc_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sqc_cost_summary) <- c("cost_1", "cost_0.1", "cost_0.01")

LC_sqc_time_summary <- matrix(LC_sqc_time,nrow = nrow(initial_weight), ncol = length(learn_rate) )  
colnames(LC_sqc_time_summary, do.NULL = TRUE, prefix = "col")
colnames(LC_sqc_time_summary) <- c("time_1", "time_0.1", "time_0.01" )

write_csv(as.data.frame(LC_sqc_cost_summary), "processed4/LC_sqc_cost_summary.csv" )
write_csv(as.data.frame(LC_sqc_time_summary), "processed4/LC_sqc_time_summary.csv" )
```
## M-estimators (welsch) loss function
### Set up function
#### Iteration function
```{r}
Fn_ME <- function(A,B){
  vector.w <- A
  matrix.Y <- as.matrix(B)
  method_no <- ncol(matrix.Y)
  alt_no <- nrow(matrix.Y)
  vector.z <- matrix.Y %*% vector.w
  
  # parameter initialization
  tol <- 10e-10 # tolerance based on which the main loop is terminated
  iter_max <- 10e5 # maximum number of iteration
  t <- 0        # iteration indicator
  alpha <- rep(0,times= ncol(matrix.Y))
  Error_norm <- rep(0,times= ncol(matrix.Y))
  
  while(t < iter_max){
    Error <- matrix.Y - repmat(vector.z,1,method_no)
    
    for (i in 1: method_no) {
    Error_norm[i] <- sqrt(sum(Error[,i]^2))
    }
    
    if(sum(Error_norm) == 0){
      break
    }
    
    sigma_square <- sum(Error_norm^2)/(2*alt_no)   # the formula used in (Mohammadi and Rezaie,2020) is not correct
    
    # update alpha
    alpha_old <- alpha
    
    for (i in 1: method_no) {
      alpha[i] <- exp(-(Error_norm[i])^2/(sigma_square))
    }
    
    # update vector.z
    vector.z_old <- vector.z

    for (i in 1: method_no) {
      vector.w[i] <- alpha[i] / sum(alpha)
    }
    vector.z <- matrix.Y %*% vector.w
    
    # convergence conditions
    if(norm(matrix(alpha-alpha_old), "2") < tol && norm(matrix(vector.z-vector.z_old), "2") < tol ){
      break
    }
    
    if(any(vector.w < 0)){
      break
    }
    # update iteration
    t = t + 1
    
    # if(iteration == 1){
    #   break
    # }
  }
  output_list <- list("iteration" = t, "sigma_square" = sigma_square, "alpha_old" = alpha_old,"alpha" = alpha, "vector.w" = vector.w, "vector.z"  = vector.z, "vector.z_old"  = vector.z_old)
  
  return(output_list)
}
```

#### Cost function
```{r}
Fn_ME_cost <- function(A, B){
  vector.z <- as.matrix(A)
  matrix.Y <- as.matrix(B)
  Error_norm <- rep(0,times= ncol(matrix.Y))
  J <- rep(0,times = ncol(matrix.Y))
  
  Error <- matrix.Y - repmat(vector.z,1,ncol(matrix.Y))
  for (i in 1: ncol(matrix.Y)) {
    Error_norm[i] <- sqrt(sum(Error[,i]^2))
  }
  
  sigma_square <- sum(Error_norm^2)/ (2*nrow(matrix.Y)*ncol(matrix.Y))
  
  for (i in 1: ncol(matrix.Y)) {
    J[i] <- sum(1-exp(-sum(Error[,i]^2)/sigma_square))
  }

  cost <- sum(J)/(ncol(matrix.Y)*nrow(matrix.Y))
}
```
### Supply risk
#### Run the iteration function
```{r}
# initialization
ME_sr_time <- matrix(, nrow = nrow(initial_weight), ncol = 1)
ME_sr_w <- matrix(, nrow = nrow(initial_weight), ncol = ncol(initial_weight))
ME_sr_z <- matrix(, nrow = nrow(initial_weight), ncol = nrow(agg_sr_df))

for (j in 1:nrow(initial_weight)) {
start_time <- Sys.time()
ME_sr  <- Fn_ME(matrix(data.matrix(initial_weight[j,])), agg_sr_df )
end_time <- Sys.time()
ME_sr_time[j,] <- end_time - start_time
ME_sr_w[j,] <- matrix(unlist(ME_sr[5]))
ME_sr_z[j,] <- matrix(unlist(ME_sr[7]))
}
# save the result
# write_csv(as.data.frame(ME_sr_time), "processed4/ME_sr_time.csv" )
write_csv(as.data.frame(ME_sr_w), "processed4/ME_sr_w.csv" )
write_csv(as.data.frame(ME_sr_z), "processed4/ME_sr_z.csv" )
```
#### Run the cost function
```{r}
ME_sr_cost <- rep(0,times = nrow(ME_sr_z))
for (i in 1:nrow(ME_sr_z)) {
  A <- data.matrix(ME_sr_z[i,])
  ME_sr_cost[i] <- Fn_ME_cost(A, agg_sr_df)
}
# ME_sr_cost
# write_csv(as.data.frame(ME_sr_cost), "processed4/ME_sr_cost.csv" )
```
#### Cost and time summary
```{r}
ME_sr_cost_summary <- matrix(ME_sr_cost,nrow = nrow(initial_weight), ncol = 1)
colnames(ME_sr_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sr_cost_summary) <- c("cost")

ME_sr_time_summary <- matrix(ME_sr_time,nrow = nrow(initial_weight), ncol = 1 )  
colnames(ME_sr_time_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sr_time_summary) <- c("time" )

write_csv(as.data.frame(ME_sr_cost_summary), "processed4/ME_sr_cost_summary.csv" )
write_csv(as.data.frame(ME_sr_time_summary), "processed4/ME_sr_time_summary.csv" )
```
### Profit impact
#### Run the iteration function
```{r}
# initialization
ME_pi_time <- matrix(, nrow = nrow(initial_weight), ncol = 1)
ME_pi_w <- matrix(, nrow = nrow(initial_weight), ncol = ncol(initial_weight))
ME_pi_z <- matrix(, nrow = nrow(initial_weight), ncol = nrow(agg_pi_df))

for (j in 1:nrow(initial_weight)) {
start_time <- Sys.time()
ME_pi  <- Fn_ME(matrix(data.matrix(initial_weight[j,])), agg_pi_df )
end_time <- Sys.time()
ME_pi_time[j,] <- end_time - start_time
ME_pi_w[j,] <- matrix(unlist(ME_pi[5]))
ME_pi_z[j,] <- matrix(unlist(ME_pi[7]))
}
```
```{r}
# save the result
# write_csv(as.data.frame(ME_pi_time), "processed4/ME_pi_time.csv" )
write_csv(as.data.frame(ME_pi_w), "processed4/ME_pi_w.csv" )
write_csv(as.data.frame(ME_pi_z), "processed4/ME_pi_z.csv" )
```

#### Run the cost function
```{r}
# caMEulate the cost for each setting
ME_pi_cost <- rep(0,times = nrow(ME_pi_z))
for (i in 1:nrow(ME_pi_z)) {
  A <- data.matrix(ME_pi_z[i,])
  ME_pi_cost[i] <- Fn_ME_cost(A, agg_pi_df)
}
# ME_pi_cost
# write_csv(as.data.frame(ME_pi_cost), "processed4/ME_pi_cost.csv" )
```
#### Cost and time summary
```{r}
ME_pi_cost_summary <- matrix(ME_pi_cost,nrow = nrow(initial_weight), ncol = 1)
colnames(ME_pi_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_pi_cost_summary) <- c("cost")

ME_pi_time_summary <- matrix(ME_pi_time,nrow = nrow(initial_weight), ncol = 1 )  
colnames(ME_pi_time_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_pi_time_summary) <- c("time" )

write_csv(as.data.frame(ME_pi_cost_summary), "processed4/ME_pi_cost_summary.csv" )
write_csv(as.data.frame(ME_pi_time_summary), "processed4/ME_pi_time_summary.csv" )
```
### Supplier willingness
#### Run the iteration function
```{r}
# initialization
ME_sw_time <- matrix(, nrow = nrow(initial_weight), ncol = 1)
ME_sw_w <- matrix(, nrow = nrow(initial_weight), ncol = ncol(initial_weight))
ME_sw_z <- matrix(, nrow = nrow(initial_weight), ncol = nrow(agg_sw_df))

for (j in 1:nrow(initial_weight)) {
start_time <- Sys.time()
ME_sw  <- Fn_ME(matrix(data.matrix(initial_weight[j,])), agg_sw_df )
end_time <- Sys.time()
ME_sw_time[j,] <- end_time - start_time
ME_sw_w[j,] <- matrix(unlist(ME_sw[5]))
ME_sw_z[j,] <- matrix(unlist(ME_sw[7]))
}
```
```{r}
# save the result
# write_csv(as.data.frame(ME_sw_time), "processed4/ME_sw_time.csv" )
write_csv(as.data.frame(ME_sw_w), "processed4/ME_sw_w.csv" )
write_csv(as.data.frame(ME_sw_z), "processed4/ME_sw_z.csv" )
```

#### Run the cost function
```{r}
ME_sw_cost <- rep(0,times = nrow(ME_sw_z))
for (i in 1:nrow(ME_sw_z)) {
  A <- data.matrix(ME_sw_z[i,])
  ME_sw_cost[i] <- Fn_ME_cost(A, agg_sw_df)
}
# ME_sw_cost
# write_csv(as.data.frame(ME_sw_cost), "processed4/ME_sw_cost.csv" )
```
#### Cost and time summary
```{r}
ME_sw_cost_summary <- matrix(ME_sw_cost,nrow = nrow(initial_weight), ncol = 1)
colnames(ME_sw_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sw_cost_summary) <- c("cost")

ME_sw_time_summary <- matrix(ME_sw_time,nrow = nrow(initial_weight), ncol = 1 )  
colnames(ME_sw_time_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sw_time_summary) <- c("time" )

write_csv(as.data.frame(ME_sw_cost_summary), "processed4/ME_sw_cost_summary.csv" )
write_csv(as.data.frame(ME_sw_time_summary), "processed4/ME_sw_time_summary.csv" )
```
### Supplier quality capability
#### Run the iteration function
```{r}
# initialization
ME_sqc_time <- matrix(, nrow = nrow(initial_weight), ncol = 1)
ME_sqc_w <- matrix(, nrow = nrow(initial_weight), ncol = ncol(initial_weight))
ME_sqc_z <- matrix(, nrow = nrow(initial_weight), ncol = nrow(agg_sqc_df))

for (j in 1:nrow(initial_weight)) {
start_time <- Sys.time()
ME_sqc  <- Fn_ME(matrix(data.matrix(initial_weight[j,])), agg_sqc_df )
end_time <- Sys.time()
ME_sqc_time[j,] <- end_time - start_time
ME_sqc_w[j,] <- matrix(unlist(ME_sqc[5]))
ME_sqc_z[j,] <- matrix(unlist(ME_sqc[7]))
}
```
```{r}
# save the result
# write_csv(as.data.frame(ME_sqc_time), "processed4/ME_sqc_time.csv" )
write_csv(as.data.frame(ME_sqc_w), "processed4/ME_sqc_w.csv" )
write_csv(as.data.frame(ME_sqc_z), "processed4/ME_sqc_z.csv" )
```

#### Run the cost function
```{r}
ME_sqc_cost <- rep(0,times = nrow(ME_sqc_z))
for (i in 1:nrow(ME_sqc_z)) {
  A <- data.matrix(ME_sqc_z[i,])
  ME_sqc_cost[i] <- Fn_ME_cost(A, agg_sqc_df)
}
# ME_sqc_cost
# write_csv(as.data.frame(ME_sqc_cost), "processed4/ME_sqc_cost.csv" )
```
#### Cost and time summary
```{r}
ME_sqc_cost_summary <- matrix(ME_sqc_cost,nrow = nrow(initial_weight), ncol = 1)
colnames(ME_sqc_cost_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sqc_cost_summary) <- c("cost")

ME_sqc_time_summary <- matrix(ME_sqc_time,nrow = nrow(initial_weight), ncol = 1 )  
colnames(ME_sqc_time_summary, do.NULL = TRUE, prefix = "col")
colnames(ME_sqc_time_summary) <- c("time" )

write_csv(as.data.frame(ME_sqc_cost_summary), "processed4/ME_sqc_cost_summary.csv" )
write_csv(as.data.frame(ME_sqc_time_summary), "processed4/ME_sqc_time_summary.csv" )
```




