---
title: "Aggregation Summary"
# output: html_notebook
author:
  - name: Qiuping Ma
date: "`r Sys.Date()`"
# creative_commons: CC BY-NC
output:
  html_notebook:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: paper
    highlight: tango
    chunk_output_type: inline
---

# Introduction
With the aggregation results, we would like to compare the performance of aggregation models associated with different loss functions. However, aggregation models can not be compared based on the value of loss functions because of different magnitude. We first plot the results based on PPM-SPM model for better illustration. As we can see, the plots show big difference with each other. But still we cannot figure out which one is better. Thus, we propose two generalized assessment measures in order to (1) assess the performance of an individual aggregation model, and (ii) do the comparion analysis among all aggregation models.

# Preparation

## Set working directory
For operation simplicity, we set the working directory as below.
```{r}
setwd("C:/Users/au630301/Documents/00.Qiuping/2nd Paper/code")
getwd()
```
## Load the package
```{r eval = FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if(!require("ggpubr")) install.packages("ggpubr")
library(ggpubr)
```
## 

### Load the aggregation result $z$
```{r}
agg_L2   <- read_csv("processed4/agg_L2.csv")
L1_sr_z  <- read_csv("processed4/L1_sr_z.csv")
L1_pi_z  <- read_csv("processed4/L1_pi_z.csv")
L1_sw_z  <- read_csv("processed4/L1_sw_z.csv")
L1_sqc_z <- read_csv("processed4/L1_sqc_z.csv")
LC_sr_z  <- read_csv("processed4/LC_sr_z.csv")
LC_pi_z  <- read_csv("processed4/LC_pi_z.csv")
LC_sw_z  <- read_csv("processed4/LC_sw_z.csv")
LC_sqc_z <- read_csv("processed4/LC_sqc_z.csv")
ME_sr_z  <- read_csv("processed4/ME_sr_z.csv")
ME_pi_z  <- read_csv("processed4/ME_pi_z.csv")
ME_sw_z  <- read_csv("processed4/ME_sw_z.csv")
ME_sqc_z <- read_csv("processed4/ME_sqc_z.csv")
```
### Load the optimal weigh $w$
```{r}
L1_sr_w  <- read_csv("processed4/L1_sr_w.csv")
L1_pi_w  <- read_csv("processed4/L1_pi_w.csv")
L1_sw_w  <- read_csv("processed4/L1_sw_w.csv")
L1_sqc_w <- read_csv("processed4/L1_sqc_w.csv")
LC_sr_w  <- read_csv("processed4/LC_sr_w.csv")
LC_pi_w  <- read_csv("processed4/LC_pi_w.csv")
LC_sw_w  <- read_csv("processed4/LC_sw_w.csv")
LC_sqc_w <- read_csv("processed4/LC_sqc_w.csv")
ME_sr_w  <- read_csv("processed4/ME_sr_w.csv")
ME_pi_w  <- read_csv("processed4/ME_pi_w.csv")
ME_sw_w  <- read_csv("processed4/ME_sw_w.csv")
ME_sqc_w <- read_csv("processed4/ME_sqc_w.csv")
```
With L2 loss function, we get unique result. As for the other 3 loss functions (L1, LOG-COSH, and ME ), we use 3 learning rate (1, 0.1, 0.01) and 100 different scenarios of criteria weight.
Given that we should minimize the objective function, we search for the optimal learning rate and criteria weight with minimal cost.
# Aggregation summary
### L1 loss
```{r}
L1_sr_cost_summary  <- read_csv("processed4/L1_sr_cost_summary.csv")
locate_L1_sr <- which(L1_sr_cost_summary == min(L1_sr_cost_summary), arr.ind = T, useNames = T)
L1_sr_z_star <-matrix(L1_sr_z[locate_L1_sr[1],])
L1_sr_w_star <-matrix(L1_sr_w[locate_L1_sr[1],])
```
```{r}
locate_L1_sr

```

```{r}
which(L1_sr_cost_summary == min(L1_sr_cost_summary), arr.ind = T, useNames = T)
```

```{r}
L1_pi_cost_summary  <- read_csv("processed4/L1_pi_cost_summary.csv")
locate_L1_pi <- which(L1_pi_cost_summary == min(L1_pi_cost_summary), arr.ind = T, useNames = T)
L1_pi_z_star <-matrix(L1_pi_z[locate_L1_pi[1],])
L1_pi_w_star <-matrix(L1_pi_w[locate_L1_pi[1],])
```
```{r}
L1_sw_cost_summary  <- read_csv("processed4/L1_sw_cost_summary.csv")
locate_L1_sw <- which(L1_sw_cost_summary == min(L1_sw_cost_summary), arr.ind = T, useNames = T)
L1_sw_z_star <-matrix(L1_sw_z[locate_L1_sw[1],])
L1_sw_w_star <-matrix(L1_sw_w[locate_L1_sw[1],])
```
```{r}
L1_sqc_cost_summary  <- read_csv("processed4/L1_sqc_cost_summary.csv")
locate_L1_sqc <- which(L1_sqc_cost_summary == min(L1_sqc_cost_summary), arr.ind = T, useNames = T)
L1_sqc_z_star <-matrix(L1_sqc_z[locate_L1_sqc[1],])
L1_sqc_w_star <-matrix(L1_sqc_w[locate_L1_sqc[1],])
```
```{r}
# summary
L1_z_star <- cbind(as.data.frame(matrix(unlist(L1_sr_z_star))), as.data.frame(matrix(unlist(L1_pi_z_star))), as.data.frame(matrix(unlist(L1_sw_z_star))), as.data.frame(matrix(unlist(L1_sqc_z_star))))
L1_w_star <- cbind(as.data.frame(matrix(unlist(L1_sr_w_star))), as.data.frame(matrix(unlist(L1_pi_w_star))), as.data.frame(matrix(unlist(L1_sw_w_star))), as.data.frame(matrix(unlist(L1_sqc_w_star))))
write_csv(L1_z_star, "processed4/L1_z_star.csv" )
write_csv(L1_w_star, "processed4/L1_w_star.csv" )
```
### Log-cosh loss
```{r}
LC_sr_cost_summary  <- read_csv("processed4/LC_sr_cost_summary.csv")
locate_LC_sr <- which(LC_sr_cost_summary == min(LC_sr_cost_summary), arr.ind = T, useNames = T)
LC_sr_z_star <-matrix(LC_sr_z[locate_LC_sr[1],])
LC_sr_w_star <-matrix(LC_sr_w[locate_LC_sr[1],])
```
```{r}
LC_pi_cost_summary  <- read_csv("processed4/LC_pi_cost_summary.csv")
locate_LC_pi <- which(LC_pi_cost_summary == min(LC_pi_cost_summary), arr.ind = T, useNames = T)
LC_pi_z_star <-matrix(LC_pi_z[locate_LC_pi[1],])
LC_pi_w_star <-matrix(LC_pi_w[locate_LC_pi[1],])
```
```{r}
LC_sw_cost_summary  <- read_csv("processed4/LC_sw_cost_summary.csv")
locate_LC_sw <- which(LC_sw_cost_summary == min(LC_sw_cost_summary), arr.ind = T, useNames = T)
LC_sw_z_star <-matrix(LC_sw_z[locate_LC_sw[1],])
LC_sw_w_star <-matrix(LC_sw_w[locate_LC_sw[1],])
```
```{r}
LC_sqc_cost_summary  <- read_csv("processed4/LC_sqc_cost_summary.csv")
locate_LC_sqc <- which(LC_sqc_cost_summary == min(LC_sqc_cost_summary), arr.ind = T, useNames = T)
LC_sqc_z_star <-matrix(LC_sqc_z[locate_LC_sqc[1],])
LC_sqc_w_star <-matrix(LC_sqc_w[locate_LC_sqc[1],])
```
```{r}
# summary
LC_z_star <- cbind(as.data.frame(matrix(unlist(LC_sr_z_star))), as.data.frame(matrix(unlist(LC_pi_z_star))), as.data.frame(matrix(unlist(LC_sw_z_star))), as.data.frame(matrix(unlist(LC_sqc_z_star))))
LC_w_star <- cbind(as.data.frame(matrix(unlist(LC_sr_w_star))), as.data.frame(matrix(unlist(LC_pi_w_star))), as.data.frame(matrix(unlist(LC_sw_w_star))), as.data.frame(matrix(unlist(LC_sqc_w_star))))
write_csv(LC_z_star, "processed4/LC_z_star.csv" )
write_csv(LC_w_star, "processed4/LC_w_star.csv" )
```
### ME loss
```{r}
ME_sr_cost_summary  <- read_csv("processed4/ME_sr_cost_summary.csv")
locate_ME_sr <- which(ME_sr_cost_summary == min(ME_sr_cost_summary), arr.ind = T, useNames = T)
ME_sr_z_star <-matrix(ME_sr_z[locate_ME_sr[1],])
ME_sr_w_star <-matrix(ME_sr_w[locate_ME_sr[1],])
```
```{r}
ME_pi_cost_summary  <- read_csv("processed4/ME_pi_cost_summary.csv")
locate_ME_pi <- which(ME_pi_cost_summary == min(ME_pi_cost_summary), arr.ind = T, useNames = T)
ME_pi_z_star <-matrix(ME_pi_z[locate_ME_pi[1],])
ME_pi_w_star <-matrix(ME_pi_w[locate_ME_pi[1],])
```
```{r}
ME_sw_cost_summary  <- read_csv("processed4/ME_sw_cost_summary.csv")
locate_ME_sw <- which(ME_sw_cost_summary == min(ME_sw_cost_summary), arr.ind = T, useNames = T)
ME_sw_z_star <-matrix(ME_sw_z[locate_ME_sw[1],])
ME_sw_w_star <-matrix(ME_sw_w[locate_ME_sw[1],])
```
```{r}
ME_sqc_cost_summary  <- read_csv("processed4/ME_sqc_cost_summary.csv")
locate_ME_sqc <- which(ME_sqc_cost_summary == min(ME_sqc_cost_summary), arr.ind = T, useNames = T)
ME_sqc_z_star <-matrix(ME_sqc_z[locate_ME_sqc[1],])
ME_sqc_w_star <-matrix(ME_sqc_w[locate_ME_sqc[1],])
```
```{r}
# summary
ME_z_star <- cbind(as.data.frame(matrix(unlist(ME_sr_z_star))), as.data.frame(matrix(unlist(ME_pi_z_star))), as.data.frame(matrix(unlist(ME_sw_z_star))), as.data.frame(matrix(unlist(ME_sqc_z_star))))
ME_w_star <- cbind(as.data.frame(matrix(unlist(ME_sr_w_star))), as.data.frame(matrix(unlist(ME_pi_w_star))), as.data.frame(matrix(unlist(ME_sw_w_star))), as.data.frame(matrix(unlist(ME_sqc_w_star))))
write_csv(ME_z_star, "processed4/ME_z_star.csv" )
write_csv(ME_w_star, "processed4/ME_w_star.csv" )
```

### Aggregation summary on z_star
```{r}
# summary on z_star
z_star_initial <- cbind(agg_L2, L1_z_star, LC_z_star, ME_z_star )
z_star <- z_star_initial[, c(1,2,6,10,14,3,7,11,15,4,8,12,16,5,9,13,17)]
colnames(z_star) <- c("Supplier_ID", "SR_L2","SR_L1", "SR_LC", "SR_ME", "PI_L2","PI_L1", "PI_LC", "PI_ME", "SW_L2","SW_L1", "SW_LC", "SW_ME", "SQC_L2","SQC_L1", "SQC_LC", "SQC_ME")
z_star_output <- z_star
z_star_output[, 2:17] <- round(z_star_output[, 2:17],3)
write_csv(z_star, "processed4/z_star.csv" )
write_csv(z_star_output, "processed4/z_star_output.csv" )
```

```{r}
# for beneficial aggregation score
norm_minmax <- function(x){
  (x- min(x)) /(max(x)-min(x))
}
```
```{r}
# normalization on z_star
z_star_norm <- z_star
z_star_norm_initial <- apply(z_star[,-1], 2, norm_minmax)
z_star_norm[,-1] <- z_star_norm_initial
z_star_norm_output <- z_star_norm
z_star_norm_output[,-1]<- round(z_star_norm_initial,3)
z_star_norm
z_star_norm_output
write_csv(z_star_norm, "processed4/z_star_norm.csv" )
write_csv(z_star_norm_output, "processed4/z_star_norm_output.csv" )
```

### Aggregation summary on w_star
```{r}
if(!require("pracma")) install.packages("pracma")
library("pracma")
```
```{r}
method_no <- 6
L2_w_star <- repmat(matrix(rep(1/method_no,method_no)),1,4)
method_name <- matrix(c("M1", "M2", "M3", "M4", "M5", "M6"))
w_star_initial <- cbind(method_name, L2_w_star, L1_w_star, LC_w_star, ME_w_star ) 
w_star <- w_star_initial[, c(1,2,6,10,14,3,7,11,15,4,8,12,16,5,9,13,17)]  
w_star_output <- w_star
w_star_output[,-1] <- round(w_star_output[,-1],3)
colnames(w_star) <- c("Method_ID", "SR_L2","SR_L1", "SR_LC", "SR_ME", "PI_L2","PI_L1", "PI_LC", "PI_ME", "SW_L2","SW_L1", "SW_LC", "SW_ME", "SQC_L2","SQC_L1", "SQC_LC", "SQC_ME")
write_csv(w_star, "processed4/w_star.csv" )     
write_csv(w_star_output, "processed4/w_star_output.csv" )  
w_star
w_star_output
```
# Comparision analysis
### Load the MCDM results
```{r}
MCDM_result_norm_new   <- read_csv("processed4/MCDM_result_norm_new.csv")
```

### Spearman’s correlation coefficient function
```{r}
  rho <- function(A, B){
    vector.A <- apply(-A, 2, rank)
    vector.B <- apply(-repmat( matrix(B),1,ncol(vector.A)), 2, rank)
    
    rho <- rep(0,times= ncol(vector.A))  # 6
    R_square <- (vector.A-vector.B)^2
    
    
    for (i in 1 : ncol(vector.A)) {
      rho[i] <- 1 - (6*sum(R_square[,i]))/(nrow(vector.A)^3-nrow(vector.A))
    }
    return(rho)
  }
```


```{r}
#test
#  vector.A <- apply(-MCDM_result_norm_new[,2:7], 2, rank)
#  #vector.A
#  vector.B <- apply(-repmat( matrix(z_star_norm$SR_L2),1,ncol(vector.A)), 2, rank)
#  #vector.B 
#  
#  
#  rho <- rep(0,times= ncol(vector.A))  # 6
#   R_square <- (vector.A-vector.B)^2
# 
#  for (i in 1 : ncol(vector.A)) {
#    rho[i] <- 1 - (6*sum(R_square[,i]))/(nrow(vector.A)^3-nrow(vector.A))
#  }
#  rho
# a <- sum(R_square[,1])
# a
# b <- 6*sum(R_square[,1])
# b
# 1-b/(100^3-100)
```


### Trust level function
```{r}
  trust_level <- function(A,B){
    vector.weight <- A
    vector.rho <- matrix(B)
    TL <- sum(vector.weight*vector.rho)
  }
```

### Do comparison analysis
#### L2 loss function
```{r}
rho_L2_sr <-  rho(MCDM_result_norm_new[,2:7],  z_star_norm$SR_L2)
rho_L2_pi <-  rho(MCDM_result_norm_new[,8:13],  z_star_norm$PI_L2)
rho_L2_sw <-  rho(MCDM_result_norm_new[,14:19], z_star_norm$SW_L2)
rho_L2_sqc <- rho(MCDM_result_norm_new[,20:25], z_star_norm$SQC_L2)

rho_L2_sr
rho_L2_pi
rho_L2_sw
rho_L2_sqc

CI_L2_sr <-  mean(rho_L2_sr)
CI_L2_pi <-  mean(rho_L2_pi)
CI_L2_sw <-  mean(rho_L2_sw)
CI_L2_sqc <- mean(rho_L2_sqc)

CI_L2_sr
CI_L2_pi
CI_L2_sw
CI_L2_sqc

TL_L2_sr <-  trust_level(w_star$SR_L2, rho_L2_sr)/sum(w_star$SR_L2)
TL_L2_pi <-  trust_level(w_star$PI_L2, rho_L2_pi)/sum(w_star$PI_L2)
TL_L2_sw <-  trust_level(w_star$SW_L2, rho_L2_sw)/sum(w_star$SW_L2)
TL_L2_sqc <- trust_level(w_star$SQC_L2, rho_L2_sqc)/sum(w_star$SQC_L2)

TL_L2_sr
TL_L2_pi
TL_L2_sw
TL_L2_sqc 
```

#### L1 loss function
```{r}
rho_L1_sr <-  rho(MCDM_result_norm_new[,2:7],  z_star_norm$SR_L1)
rho_L1_pi <-  rho(MCDM_result_norm_new[,8:13],  z_star_norm$PI_L1)
rho_L1_sw <-  rho(MCDM_result_norm_new[,14:19], z_star_norm$SW_L1)
rho_L1_sqc <- rho(MCDM_result_norm_new[,20:25], z_star_norm$SQC_L1)

rho_L1_sr
rho_L1_pi
rho_L1_sw
rho_L1_sqc

CI_L1_sr <-  mean(rho_L1_sr)
CI_L1_pi <-  mean(rho_L1_pi)
CI_L1_sw <-  mean(rho_L1_sw)
CI_L1_sqc <- mean(rho_L1_sqc)

CI_L1_sr
CI_L1_pi
CI_L1_sw
CI_L1_sqc

TL_L1_sr <-  trust_level(w_star$SR_L1, rho_L1_sr)/sum(w_star$SR_L1)
TL_L1_pi <-  trust_level(w_star$PI_L1, rho_L1_pi)/sum(w_star$PI_L1)
TL_L1_sw <-  trust_level(w_star$SW_L1, rho_L1_sw)/sum(w_star$SW_L1)
TL_L1_sqc <- trust_level(w_star$SQC_L1, rho_L1_sqc)/sum(w_star$SQC_L1)

TL_L1_sr
TL_L1_pi
TL_L1_sw
TL_L1_sqc 
```

#### LC loss function
```{r}
rho_LC_sr <-  rho(MCDM_result_norm_new[,2:7],  z_star_norm$SR_LC)
rho_LC_pi <-  rho(MCDM_result_norm_new[,8:13],  z_star_norm$PI_LC)
rho_LC_sw <-  rho(MCDM_result_norm_new[,14:19], z_star_norm$SW_LC)
rho_LC_sqc <- rho(MCDM_result_norm_new[,20:25], z_star_norm$SQC_LC)

rho_LC_sr
rho_LC_pi
rho_LC_sw
rho_LC_sqc

CI_LC_sr <-  mean(rho_LC_sr)
CI_LC_pi <-  mean(rho_LC_pi)
CI_LC_sw <-  mean(rho_LC_sw)
CI_LC_sqc <- mean(rho_LC_sqc)

CI_LC_sr
CI_LC_pi
CI_LC_sw
CI_LC_sqc

TL_LC_sr <-  trust_level(w_star$SR_LC, rho_LC_sr)/sum(w_star$SR_LC)
TL_LC_pi <-  trust_level(w_star$PI_LC, rho_LC_pi)/sum(w_star$PI_LC)
TL_LC_sw <-  trust_level(w_star$SW_LC, rho_LC_sw)/sum(w_star$SW_LC)
TL_LC_sqc <- trust_level(w_star$SQC_LC, rho_LC_sqc)/sum(w_star$SQC_LC)

TL_LC_sr
TL_LC_pi
TL_LC_sw
TL_LC_sqc 
```
#### ME loss function
```{r}
rho_ME_sr <-  rho(MCDM_result_norm_new[,2:7],  z_star_norm$SR_ME)
rho_ME_pi <-  rho(MCDM_result_norm_new[,8:13],  z_star_norm$PI_ME)
rho_ME_sw <-  rho(MCDM_result_norm_new[,14:19], z_star_norm$SW_ME)
rho_ME_sqc <- rho(MCDM_result_norm_new[,20:25], z_star_norm$SQC_ME)

rho_ME_sr
rho_ME_pi
rho_ME_sw
rho_ME_sqc

CI_ME_sr <-  mean(rho_ME_sr)
CI_ME_pi <-  mean(rho_ME_pi)
CI_ME_sw <-  mean(rho_ME_sw)
CI_ME_sqc <- mean(rho_ME_sqc)

CI_ME_sr
CI_ME_pi
CI_ME_sw
CI_ME_sqc

TL_ME_sr <-  trust_level(w_star$SR_ME, rho_ME_sr)/sum(w_star$SR_ME)
TL_ME_pi <-  trust_level(w_star$PI_ME, rho_ME_pi)/sum(w_star$PI_ME)
TL_ME_sw <-  trust_level(w_star$SW_ME, rho_ME_sw)/sum(w_star$SW_ME)
TL_ME_sqc <- trust_level(w_star$SQC_ME, rho_ME_sqc)/sum(w_star$SQC_ME)

TL_ME_sr
TL_ME_pi
TL_ME_sw
TL_ME_sqc 
```

### Final assessment 
Here we compare the consensus index and trust level with respect to the above 4 loss functions. Note that we have four dimensions, the comparison result may vary from one dimension to another.
```{r}
compar_summary <- matrix(0, nrow = 4, ncol = 9)
# consensus index
compar_summary[1,1] <- CI_L2_sr
compar_summary[2,1] <- CI_L2_pi
compar_summary[3,1] <- CI_L2_sw
compar_summary[4,1] <- CI_L2_sqc
compar_summary[1,2] <- CI_L1_sr
compar_summary[2,2] <- CI_L1_pi
compar_summary[3,2] <- CI_LC_sw
compar_summary[4,2] <- CI_L1_sqc
compar_summary[1,3] <- CI_LC_sr
compar_summary[2,3] <- CI_LC_pi
compar_summary[3,3] <- CI_LC_sw
compar_summary[4,3] <- CI_LC_sqc
compar_summary[1,4] <- CI_ME_sr
compar_summary[2,4] <- CI_ME_pi
compar_summary[3,4] <- CI_ME_sw
compar_summary[4,4] <- CI_ME_sqc

# trust level
compar_summary[1,5] <- TL_L2_sr
compar_summary[2,5] <- TL_L2_pi
compar_summary[3,5] <- TL_L2_sw
compar_summary[4,5] <- TL_L2_sqc
compar_summary[1,6] <- TL_L1_sr
compar_summary[2,6] <- TL_L1_pi
compar_summary[3,6] <- TL_L1_sw
compar_summary[4,6] <- TL_L1_sqc
compar_summary[1,7] <- TL_LC_sr
compar_summary[2,7] <- TL_LC_pi
compar_summary[3,7] <- TL_LC_sw
compar_summary[4,7] <- TL_LC_sqc
compar_summary[1,8] <- TL_ME_sr
compar_summary[2,8] <- TL_ME_pi
compar_summary[3,8] <- TL_ME_sw
compar_summary[4,8] <- TL_ME_sqc
# dimension name
compar_summary[1,9] <- "supplier risk"
compar_summary[2,9] <- "profit impact"
compar_summary[3,9] <- "supplier willingness"
compar_summary[4,9] <- "supplier quality capability"

colnames(compar_summary) <- c("CI_L2", "CI_L1","CI_LC","CI_ME", "TL_L2", "TL_L1","TL_LC","TL_ME", "dimension")
compar_summary
write_csv(as.data.frame(compar_summary), "processed4/compar_summary.csv" ) 
```

# Plot on the aggrgation result
Here we would like to visualize the aggregation result along with the six MCDM methods used before. So that we can see the performance of aggrgation models and check whether they are more reliable (output consistent results) compared with usinga single MCDM method.

## preparation
### install package
```{r}
if(!require("ggplot2")) install.packages("ggplot2")
library("ggplot2")
if(!require("repr")) install.packages("repr")
library("repr")
if(!require("reshape2")) install.packages("reshape2")
library("reshape2")
```
### load the dataset
```{r}
MCDM_result_norm_new <- read_csv("processed4/MCDM_result_norm_new.csv")
```

## Plot
### Supply Risk
```{r}
df_sr_ag <- cbind(MCDM_result_norm_new[1:10, 1:7], z_star_norm[1:10, 2:5]) %>%
  rename(M1 = M1_sr,
         M2 = M2_sr,
         M3 = M3_sr,
         M4 = M4_sr,
         M5 = M5_sr,
         M6 = M6_sr,
         AG1 = SR_L2,
         AG2 = SR_L1,
         AG3 = SR_LC,
         AG4 = SR_ME
  )

```

```{r}
df_sr_melt_ag = melt(df_sr_ag, id = "Supplier_ID")
df_sr_melt_ag
```
```{r}
df_sr_melt_ag <-df_sr_melt_ag %>%
  rename(Method = variable,
         Score = value)
df_sr_melt_ag
```
```{r}
plot_sr_ag <- ggplot(df_sr_melt_ag, aes(x = Method, y = Score, group = Supplier_ID)) + 
  geom_line() + 
  facet_wrap(Supplier_ID ~ ., nrow = 2, ncol = 5) +
  geom_point() +
  labs(
  title = "Supplier risk",
  x = "models",
  y = "Score"
  ) +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylim(0, 1)
ggsave(file="processed4/plot/plot_sr_ag.pdf",width=12, height=2.5, dpi=300)
```

### Profit impact
```{r}
df_pi_ag <- cbind(MCDM_result_norm_new[1:10, c(1,8:13)], z_star_norm[1:10, 6:9]) %>%
  rename(M1 = M1_pi,
         M2 = M2_pi,
         M3 = M3_pi,
         M4 = M4_pi,
         M5 = M5_pi,
         M6 = M6_pi,
         AG1 = PI_L2,
         AG2 = PI_L1,
         AG3 = PI_LC,
         AG4 = PI_ME
  )

```

```{r}
df_pi_melt_ag = melt(df_pi_ag, id = "Supplier_ID")
df_pi_melt_ag
```
```{r}
df_pi_melt_ag <-df_pi_melt_ag %>%
  rename(Method = variable,
         Score = value)
df_pi_melt_ag
```
```{r}
plot_pi_ag <- ggplot(df_pi_melt_ag, aes(x = Method, y = Score, group = Supplier_ID)) + 
  geom_line() + 
  facet_wrap(Supplier_ID ~ ., nrow = 2, ncol = 5) +
  geom_point() +
  labs(
  title = "Profit impact",
  x = "models",
  y = "Score"
  ) +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylim(0, 1)
ggsave(file="processed4/plot/plot_pi_ag.pdf",width=12, height=2.5, dpi=300)
```

### Supplier willingness
```{r}
df_sw_ag <- cbind(MCDM_result_norm_new[1:10, c(1,14:19)], z_star_norm[1:10, 10:13]) %>%
  rename(M1 = M1_sw,
         M2 = M2_sw,
         M3 = M3_sw,
         M4 = M4_sw,
         M5 = M5_sw,
         M6 = M6_sw,
         AG1 = SW_L2,
         AG2 = SW_L1,
         AG3 = SW_LC,
         AG4 = SW_ME
  )

```

```{r}
df_sw_melt_ag = melt(df_sw_ag, id = "Supplier_ID")
df_sw_melt_ag
```
```{r}
df_sw_melt_ag <-df_sw_melt_ag %>%
  rename(Method = variable,
         Score = value)
df_sw_melt_ag
```
```{r}
plot_sw_ag <- ggplot(df_sw_melt_ag, aes(x = Method, y = Score, group = Supplier_ID)) + 
  geom_line() + 
  facet_wrap(Supplier_ID ~ ., nrow = 2, ncol = 5) +
  geom_point() +
  labs(
  title = "Supplier willingness",
  x = "models",
  y = "Score"
  ) +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylim(0, 1)
ggsave(file="processed4/plot/plot_sw_ag.pdf",width=12, height=2.5, dpi=300)
```


### Supplier Quality Capability
```{r}
df_sqc_ag <- cbind(MCDM_result_norm_new[1:10, c(1,20:25)], z_star_norm[1:10, 14:17]) %>%
  rename(M1 = M1_sqc,
         M2 = M2_sqc,
         M3 = M3_sqc,
         M4 = M4_sqc,
         M5 = M5_sqc,
         M6 = M6_sqc,
         AG1 = SQC_L2,
         AG2 = SQC_L1,
         AG3 = SQC_LC,
         AG4 = SQC_ME
  )

```

```{r}
df_sqc_melt_ag = melt(df_sqc_ag, id = "Supplier_ID")
df_sqc_melt_ag
```
```{r}
df_sqc_melt_ag <-df_sqc_melt_ag %>%
  rename(Method = variable,
         Score = value)
df_sqc_melt_ag
```
```{r}
plot_sqc_ag <- ggplot(df_sqc_melt_ag, aes(x = Method, y = Score, group = Supplier_ID)) + 
  geom_line() + 
  facet_wrap(Supplier_ID ~ ., nrow = 2, ncol = 5) +
  geom_point() +
  #geom_path(aes(group = 5)) +
  labs(
  title = "Supplier quality capability",
  x = "models",
  y = "Score"
  ) +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylim(0, 1)
ggsave(file="processed4/plot/plot_sqc_ag.pdf",width=12, height=2.5, dpi=300)
```
```{r}
plot_sqc_ag
```


## Plot summary
```{r}
if(!require("ggpubr")) install.packages("ggpubr")
library("ggpubr")
```

```{r}
ggarrange(plot_sr_ag,plot_pi_ag, plot_sw_ag, plot_sqc_ag,
          ncol = 1, nrow = 4)
ggsave(file="processed4/plot/plot_summary_ag.pdf",width=12, height=17, dpi=300)
```

# Time summary

### Load the time summary data set
```{r}
L1_sr_time  <- read_csv("processed4/L1_sr_time_summary.csv")
L1_pi_time  <- read_csv("processed4/L1_pi_time_summary.csv")
L1_sw_time  <- read_csv("processed4/L1_sw_time_summary.csv")
L1_sqc_time <- read_csv("processed4/L1_sqc_time_summary.csv")
LC_sr_time  <- read_csv("processed4/LC_sr_time_summary.csv")
LC_pi_time  <- read_csv("processed4/LC_pi_time_summary.csv")
LC_sw_time  <- read_csv("processed4/LC_sw_time_summary.csv")
LC_sqc_time <- read_csv("processed4/LC_sqc_time_summary.csv")
ME_sr_time  <- read_csv("processed4/ME_sr_time_summary.csv")
ME_pi_time  <- read_csv("processed4/ME_pi_time_summary.csv")
ME_sw_time  <- read_csv("processed4/ME_sw_time_summary.csv")
ME_sqc_time <- read_csv("processed4/ME_sqc_time_summary.csv")
```

```{r}
time_summary_all <- vector()
time_summary_all[1] <- sum(L1_sr_time)
time_summary_all[2] <- sum(LC_sr_time)
time_summary_all[3] <- sum(ME_sr_time)
time_summary_all[4] <- sum(L1_pi_time)
time_summary_all[5] <- sum(LC_pi_time)
time_summary_all[6] <- sum(ME_pi_time)
time_summary_all[7] <- sum(L1_sw_time)
time_summary_all[8] <- sum(LC_sw_time)
time_summary_all[9] <- sum(ME_sw_time)
time_summary_all[10] <- sum(L1_sqc_time)
time_summary_all[11] <- sum(LC_sqc_time)
time_summary_all[12] <- sum(ME_sqc_time)

```

```{r}
time_summary_all
write_csv(as.data.frame(time_summary_all), "processed4/time_summary_all.csv" )
```
















